Towards Practical First-Order Model Counting

### 2024-08-14 doc/paper/paper.tex
edits

In this work, we have made several contributions. First, we have developed
algorithmic techniques to find the base cases of recursive functions generated
by \textsc{Crane}. Second, we have extended the smoothing procedure of
\textsc{ForcLift} and \textsc{Crane} to support base case formulas. Third, we
have proposed an approach to compile function definitions into C++ programs with
support for arbitrary-precision arithmetic. Lastly, we have provided
experimental evidence demonstrating that \Cranetwo{} can scale to much larger
domain sizes than \textsc{FastWFOMC} while handling more formulas than
\textsc{ForcLift}. Having FOMC algorithms that can efficiently handle large
domain sizes is especially crucial in the weighted setting. For example,
consider the `friends' instance examined in \cref{sec:experiments}, which models
a social network with friendships, smoking habits, and the probability of having
cancer. The utility of such a model would be significantly limited if
probabilities could only be efficiently computed for networks of at most
\num{1000} people.

>>>>

In this work, we present a scalable automated first-order knowledge compilation-based approach to first order model counting. The proposed approach relies on automatically generating the C++ code corresponding to the recursive functions extracted from knowledge compilation. The enusing empirical evaluatino demonstrated  that \Cranetwo{} can scale to much larger
domain sizes than \textsc{FastWFOMC} while handling more formulas than
\textsc{ForcLift}. Having FOMC algorithms that can efficiently handle large
domain sizes is especially crucial in the weighted setting. For example,
consider the `friends' instance examined in \cref{sec:experiments}, which models
a social network with friendships, smoking habits, and the probability of having
cancer. The utility of such a model would be significantly limited if
probabilities could only be efficiently computed for networks of at most
\num{1000} people.
